Make any stupid plot you want

### 2021-02-14 draft/sections/next.tex
lapsed into reading Mackinlay for notes on limitations

\subsection{What are the limitations?}
This framework is aimed at developers, not end users which is why it's equation soup only understood by physicits and mathematicians.

.  It is a way to describe the pathway from data to graphic in a

\subsection{What else needs to be implemented?}
\begin{itemize}
    \item heatmaps/ proof of concept of face simplex
    \item composition algebra
    \item boxplot - multiglyph composition
    \item debatable: non-trivial bundle like data on mobius backend
    \item interactivity 
    \item concurrent artist
    \item numpy wrapper
\end{itemize}
\begin{itemize}
    \item provisional implementation using new architecture in Matplotlib
    \item developer-aimed documentation (API + narrative)
    \item proof of concept 3rd party user-facing library with a biology partner
    \item academic paper about building visualization tools on top of the core architecture
\end{itemize}

>>>>

\subsection{What are the limitations?}
\begin{itemize}
\item is at arc level
\item is compose(encodes) and ggplot is plot(encodes, glyph)
\item can't handle figerative/semantic equivariance (this actually could be done as extension of fber)
\item is only developed against Matplotlib
\item is written against AGG/SVG
\end{itemize}
\subsection{What else needs to be implemented?}
\begin{itemize}
    \item heatmaps/ proof of concept of face simplex
    \item composition algebra
    \item boxplot - multiglyph composition
    \item debatable: non-trivial bundle like data on mobius backend
    \item interactivity 
    \item concurrent artist
    \item numpy wrapper
\end{itemize}
\begin{itemize}
    \item provisional implementation using new architecture in Matplotlib
    \item developer-aimed documentation (API + narrative)
    \item proof of concept 3rd party user-facing library with a biology partner
    \item academic paper about building visualization tools on top of the core architecture
\end{itemize}
